Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2022-03-11 paper/introduction.tex

Modern D-T reactors rely on tritium breeding blankets, specialized
layers of material which partially line the reactor and produce tritium upon
neutron bombardment, e.g.~by 
\begin{eqnarray}
	\isotope[1][0]{n} + \hspace{3pt} \isotope[6][3]{Li} 
	&\longrightarrow \hspace{3pt} 
	\isotope[3][1]{T} + \hspace{3pt}\isotope[4][2]{He} \\
	\isotope[1][0]{n} + \hspace{3pt} \isotope[7][3]{Li} 
	&\longrightarrow \hspace{3pt} 
	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}
\end{eqnarray}%
where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. The TBR is defined as the ratio
between tritium generation in the breeding blanket and consumption in the
reactor, whose description in Paramak is facilitated by 2~classes of parameters
(exhaustively listed in~\Tref{tbl:params}). While the geometry of a given
reactor is described by continuous parameters, material selections are specified
by discrete categorical parameters. For all parameters, we have attempted to cover the full theoretical range of values even where those values are practically infeasible with current technology (e.g. packing fractions close to 1). Simulating broadly around typical values of parameters is necessary to construct the most accurate model of the typical range, and also aids in demonstrating the robustness of constructed models.

>>>>

Modern D-T reactors rely on tritium breeding blankets, specialized
layers of material which partially line the reactor and produce tritium upon
neutron bombardment, e.g.~by 
\begin{eqnarray}
	\isotope[1][0]{n} + \hspace{3pt} \isotope[6][3]{Li} 
	&\longrightarrow \hspace{3pt} 
	\isotope[3][1]{T} + \hspace{3pt}\isotope[4][2]{He} \\
	\isotope[1][0]{n} + \hspace{3pt} \isotope[7][3]{Li} 
	&\longrightarrow \hspace{3pt} 
	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}
\end{eqnarray}%
where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. The TBR is defined as the ratio of tritium produced per source neutron
, whose description in Paramak is facilitated by 2~classes of parameters
(exhaustively listed in~\Tref{tbl:params}). While the geometry of a given
reactor is described by continuous parameters, material selections are specified
by discrete categorical parameters. For all parameters, we have attempted to cover the full theoretical range of values even where those values are practically infeasible with current technology (e.g. packing fractions close to 1). Simulating broadly around typical values of parameters is necessary to construct the most accurate model of the typical range, and also aids in demonstrating the robustness of constructed models.
